---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


```{r, include=FALSE}
options("width"=110)
tmp <- packageDescription( basename(getwd()) )
```


```{r, results='asis', echo=FALSE}
cat("##", tmp$Title)
```



```{r, include=FALSE}
filelist.R   <- list.files("R", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.tests   <- list.files("tests", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.cpp <- list.files("src", recursive = TRUE, pattern="\\.cpp$", ignore.case = TRUE, full.names = TRUE)
lines.R      <- unlist(lapply(filelist.R, readLines))
lines.tests  <- unlist(lapply(filelist.tests, readLines))
lines.cpp    <- unlist(lapply(filelist.cpp, readLines))
length.R     <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.R,  value = TRUE, invert = TRUE))
length.tests <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.tests,  value = TRUE, invert = TRUE))
length.cpp   <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.cpp,  value = TRUE, invert = TRUE))
```



**Status**


*lines of R code:* `r length.R`, *lines of test code:* `r length.tests`

[![Project Status: Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<a href="https://travis-ci.org/petermeissner/ical">
<img src="https://api.travis-ci.org/petermeissner/ical.svg?branch=master">
<a/>
<a href="https://cran.r-project.org/package=ical">
<img src="http://www.r-pkg.org/badges/version/ical">
</a>
<a href="https://codecov.io/gh/petermeissner/ical">
  <img src="https://codecov.io/gh/petermeissner/ical/branch/master/graph/badge.svg" alt="Codecov" />
</a>
<img src="http://cranlogs.r-pkg.org/badges/grand-total/ical">
<img src="http://cranlogs.r-pkg.org/badges/ical">





**Development version**

```{r, include=FALSE}
source_files <- 
  grep(
    "/R/|/src/|/tests/",
    list.files(recursive = TRUE, full.names = TRUE), 
    value = TRUE
  )
last_change <- 
  as.character(
    format(max(file.info(source_files)$mtime), tz="UTC")
  )
```


```{r, results='asis', echo=FALSE}
cat(tmp$Version)
cat(" - ")
cat(stringr::str_replace(last_change, " ", " / "))
```

**Description**

```{r, results='asis', echo=FALSE}
cat(tmp$Description)
```


**License**

```{r, results='asis', echo=FALSE}
cat(tmp$License, "<br>")
cat(tmp$Author)
```


**Contribution - AKA The-Think-Twice-Be-Nice-Rule**

Please note that this project is released with a Contributor Code of Conduct. By participating in this project you agree to abide by its terms:

http://contributor-covenant.org/version/1/0/0/


## Installation

**Installation and start - stable version**

```{r, eval=FALSE}
install.packages("ical")

library(ical)
```


**Installation and start - development version**

```{r, eval=FALSE}
if (!require("V8")) {
  install.packages("V8")
}

devtools::install_github("petermeissner/ical")

library(ical)
```


## Usage


**laoding package**
```{r}
library(ical)
```

**get path to a ical file**

```{r}
ical_file <- system.file("birthdays.ics", package = "ical")
```


**parse file to data.frame**

```{r}
ical_parse_df(ical_file)
```



